\section*{Description}

PEPE (Project Elaborating Program with Extension) is a web-based
collaborative project management system designed to support software
development teams throughout the entire Software Development Life Cycle
(SDLC). It provides an integrated environment that enables teams to plan,
organize, track, and manage software projects in a structured, transparent,
and efficient manner.

The system is specifically targeted at students, academic project groups,
and small software development teams who require a lightweight yet powerful
tool to manage their projects without the complexity of enterprise-level
platforms.

\section*{Objectives}

PEPE aims to: \\
\begin{itemize}[nosep]
    \item Improve team collaboration and communication.
    \item Provide a centralized platform for project planning and documentation.
    \item Enable efficient task tracking, progress monitoring, and issue management.
    \item Assist teams in meeting deadlines through proper scheduling and milestone control.
    \item Provide insights into team productivity through basic analytics and reporting.
\end{itemize}


\section*{Key Features}

\subsection*{1. Project Planning}
\begin{itemize}[nosep]
    \item Create and manage multiple projects.
    \item Define project scope, goals, milestones, and deadlines.
    \item Visualize timelines using Gantt charts.
\end{itemize}

\subsection*{2. Task Management}
\begin{itemize}[nosep]
    \item Break projects into tasks and subtasks.
    \item Assign tasks to team members.
    \item Set priorities, deadlines, and dependencies.
    \item Track task status: To Do, In Progress, Testing, Completed.
\end{itemize}

\subsection*{3. Collaboration \& Communication}
\begin{itemize}[nosep]
    \item Built-in comment system for tasks.
    \item Real-time notifications for task updates and deadlines.
    \item Activity feed to monitor project progress.
\end{itemize}

\subsection*{4. Reporting \& Analytics}
\begin{itemize}[nosep]
    \item Progress reports per project or per member.
\end{itemize}

\subsection*{5. User \& Role Management}
\begin{itemize}[nosep]
    \item Roles: Admin, Project Manager, Team Member.
    \item Access control based on roles.
\end{itemize}

\subsection*{6. Issue \& Bug Tracking (Optional)}
\begin{itemize}[nosep]
    \item Report bugs or issues via tickets.
    \item Assign severity levels.
    \item Track resolution status.
\end{itemize}

\subsection*{7. Visual Studio Code Integration with Extension (Optional)}
\begin{itemize}[nosep]
    \item Interpret \texttt{TASK} from comment in code.
    \item Assign \texttt{TASK} to \texttt{@USER} or \texttt{@ROLE} via external task
        specification file in Markdown format.
    \item Interpret \texttt{TASK} from comment in code.
\end{itemize}

\section*{Benefits}
\begin{itemize}[nosep]
    \item Reduces dependency on scattered tools like spreadsheets and chat apps.
    \item Improves project transparency and accountability.
    \item Enhances learning experience for students in team-based projects.
    \item Saves time by automating routine project management activities.
\end{itemize}

\section*{Target Users}
\begin{itemize}[nosep]
    \item University students working on capstone or group projects.
    \item Small development teams and startups.
    \item Academic instructors supervising multiple student teams.
\end{itemize}

\section*{Conclusion}

PEPE serves as a simple yet comprehensive project management solution
that bridges the gap between theory and practice in software engineering.
By providing essential planning, tracking, and collaboration features
in one unified platform, it empowers teams to deliver projects on time
with higher quality and better coordination.
